The Decreasing Orbital Period of WASP-4\lowercase{b}

### 2018-12-05 paper/ms.tex
fixed 1/(pi^2) factor in tau_e timescale
per equation 2018/12/04.3(1)

%FIXME
Could the eccentricity truly be non-zero?  The classical
tidal-circularization theory has the eccentricity shrinking with a
$1/e$-folding time of \citep[{\it e.g.}, Equation~1
of][]{dobbs-dixon_spin-orbit_2004}
\begin{equation}
  \tau_e
  = \frac{e}{|\dot{e}|}
  = \frac{2\pi Q_{\rm p}'}{63}
  \left( \frac{a}{R_{\rm p}} \right)^5
  \frac{M_{\rm p}}{M_\star}\, P .
\end{equation}
For WASP-4b, this gives an eccentricity damping timescale of $\tau_e =
28.3 (Q_{\rm p}'/10^6) \, {\rm Myr}$.  The system age appears to be
well over $1\,{\rm Gyr}$ \citep{winn_transit_2009}, so any initial
eccentricity should have been erased.

>>>>

Could the eccentricity truly be non-zero?  For WASP-4b, the
eccentricity damping timescale (Equation~\ref{eq:de_dt}) is $\tau_e =
0.29 (Q_{\rm p}'/10^5) \, {\rm Myr}$.  The system age appears to be
well over $1\,{\rm Gyr}$ \citep{winn_transit_2009}, so any initial
eccentricity should have been erased.
